Updates a Procrustes and a PCA

### 2025-04-28 Analysis/17-update_procrustes_and_PCA.Rmd
Update 17-update_procrustes_and_PCA.Rmd

@@

legend("topright", pch = c(21, 19, 21, 19), col = c("grey", "grey", "blue", "orange"), pt.cex = c(1, 0.5, 1, 0.5), legend = c("original PCA", "updated PCA", "old_spec (target)", "old_spec (results)"))
```

@@

>>>>

TODO: TRY CENTERING THE DATA BEFORE DOING THE PCA

@@

legend("topright", pch = c(21, 19, 21, 19), col = c("grey", "grey", "blue", "orange"), pt.cex = c(1, 0.5, 1, 0.5), legend = c("original PCA", "updated PCA", "old_spec (target)", "old_spec (results)"))

@@

Checking all over again with `princomp`

```{r}
## New test
library(Morpho)
library(landvR) # install from devtools::install_github("TGuillerme/landvR")

## New species (three to anchor and two new ones)
new_spec <- array(data = c(original_landmarks[,,1],
                           original_landmarks[,,2],
                           original_landmarks[,,3],
                           apply(original_landmarks, c(1,2), median),
                           apply(original_landmarks, c(1,2), min)),  dim = c(10, 3, 5))
dimnames(new_spec)[[3]] <- c(paste0("old_", c("spec1", "spec2", "spec3")), "median", "min")

## Run the PCA for the original data
proc_matrix_orig <- landvR::array.to(proc_orig$rotated, to = "matrix")
pca_orig <- prcomp(proc_matrix_orig)
princomp_orig <- princomp(landvR::array.to(proc_orig$rotated, to = "matrix"))

## THIS PIPELINE SEEMS TO WORK:

## Test the reprojection using princomp
new_gpa <- Morpho::align2procSym(proc_orig, new_spec)
new_points <- stats::predict(princomp_orig, newdata = array.to(new_gpa, to = "matrix"))
plot(original_pca$scores[,c(1,2)], col = "grey")
points(new_points[,c(1,2)], col = "orange", pch = 19)
points(original_pca$scores[c(1,2,3),c(1,2)], col = "blue", pch = 21)

## NOW NEEDS TO CHANGE FROM THE MORPHO PCA to PRINCOMP FORMAT AND BACK
```
